### 2019-03-18 reports/thesis/chapters/5_inference.tex
Appendix for inference

Return back to the sub-image example in Figure \ref{fig:inference_inferenceSubsample1_histogram}. The histogram was smoothed using a kernel density estimate \citep{parzen1962on, friedman2001elements} as shown in Figure \ref{fig:inference_inferenceSubsample1_densityEstimate}. The kernel density estimate \citep{parzen1962on} is
\begin{equation}
  \widehat{p}_Z(z)=
  \frac{1}{nh}
  \sum_{i=1}^n\phi\left(
    \dfrac{z_i-z}{h}
  \right)
  \label{eq:inference_kernel_density_estimate}
\end{equation}
where $h$ is the bandwidth. The bandwidth was chosen such that
\begin{equation}
  h = 0.9n^{-1/5}\times\text{min}\left(s_z,\text{iqr}_z/1.34\right) + 0.16
  \label{eq:inference_ourruleofthumb}
\end{equation}
where $s_z$ and $\text{iqr}_z$ are the standard deviation and interquartile range.

@@

for $r=0,1,2,3,\cdots$ until some convergence condition is met. The derivatives for the log density was obtained via the following. Recall that the kernel density estimate is
  \widehat{p}_Z(z)=

@@

    \dfrac{z_i-z}{h}
  \tag{\ref{eq:inference_kernel_density_estimate}}

@@

The kernel density estimator was only used to obtain values of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$. Thus a good bandwidth, in the context of the empirical null, is one which has good properties of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$ rather than the density estimate. Exact properties of these estimators based on the kernel density estimators can be rather complicated. For example numerous approximations were needed to show that $\widehat{\sigma}_0$ is an unbiased estimator of $\sigma_0$ to the first order, where higher order terms are functions of $\widehat{\mu}_0 - \mu_0$ and $h$. This is shown in Appendix ?.

>>>>

Return back to the sub-image example in Figure \ref{fig:inference_inferenceSubsample1_histogram}. The histogram was smoothed using a kernel density estimate \citep{parzen1962on, friedman2001elements} as shown in Figure \ref{fig:inference_inferenceSubsample1_densityEstimate}. The kernel density estimate \citep{parzen1962on} is
\begin{equation}
  \widehat{p}_Z(z)=
  \frac{1}{nh}
  \sum_{i=1}^n\phi\left(
    \dfrac{z_i-z}{h}
  \right)
  \label{eq:inference_kernel_density_estimate}
\end{equation}
where $h$ is the bandwidth. The bandwidth was chosen such that
\begin{equation}
  h = 0.9n^{-1/5}\times\text{min}\left(s_z,\text{IQR}_z/1.34\right) + 0.16
  \label{eq:inference_ourruleofthumb}
\end{equation}
where $s_z$ and $\text{iqr}_z$ are the standard deviation and interquartile range.

@@

for $r=0,1,2,3,\cdots$ until some convergence condition is met. The derivatives for the log density was obtained via the following. Recall that the kernel density estimate is $\widehat{p}_Z(z)=

@@

    \frac{z_i-z}{h}
  \right) $

@@

The kernel density estimator was only used to obtain values of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$. Thus a good bandwidth, in the context of the empirical null, is one which has good properties of $\widehat{\mu}_0$ and $\widehat{\sigma}_0$ rather than the density estimate. Exact properties of these estimators based on the kernel density estimators can be rather complicated. For example numerous approximations were needed to show that $\widehat{\sigma}_0^2$ is an unbiased estimator of $\sigma_0^2$ to the first order, where higher order terms are functions of $(\widehat{\mu}_0 - \mu_0)^2$ and $h$. This is shown in Appendix \ref{chapter:appendix_expectationNullStdEstimator}.
